---
title : Data products project presentation
subtitle : This is my project pith presentation. 
framework   : io2012 
mode        : selfcontained # {selfcontained, standalone, draft}
knit        : slidify::knit2slides
---
## Project Summary
I have built a simple miles per gallon fuel consumption app, based on the mtcars data set. The predictors I used were car weight and engine horsepower.

---
## Data set analysis
The mt cars data set has 11 variables:

```{r}
str(mtcars)
```

---
## Feature Selection
I have decided to use 2 features as mpg predictors. These features are car weight and engine horsepowers. it is possible to see that there is a strong relation between mpg and the 2 predictors, for example this is a scatterplot of mpg and weight:
```{r ,fig.width=8, fig.height=5}
plot(mtcars$wt, mtcars$mpg)
```

---
## Model Creation
I have built the model using the linear model function, and these are the results:
```{r}
fit <- lm(mpg~hp+wt, data=mtcars)
summary(fit)$r.squared
```
---

